CudeleFS: Programmable Consistency and \\Durability in a Global Namespace

### 2017-04-04 paper/sections/6_results.tex
paper: anonymize and add ivo feedback
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

This paper adheres to The Popper
Convention\footnote{\url{http://falsifiable.us}}~\cite{jimenez_popper_2016}, so
experiments presented here are available in the repository for this
article\footnote{\url{https://github.com/michaelsevilla/cudele-popper/}}.
Experiments can be examined in more detail, or even re-run, by visiting the
\texttt{[source]} link next to each figure. That link points to a Jupyter
notebook that shows the analysis and source code for that graph, which points
to an experiment and its artifacts.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/viz-decoupled.ipynb}{source}]
The performance of the CudeleFS mechanisms normalized to the runtime of the
``Append Client Journal" mechanism (the runtime of writing \(n\) file creates
to the client's in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/behavior-journal-size.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/viz-decoupled.ipynb}{source}]
In-memory client journal scales with the number of
updates.\label{fig:behavior-journal-size}}
\end{figure}

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the CudeleFS
mechanisms, normalized to the time it takes to write \(n\) file create updates
to the client's in-memory journal ({\it i.e.} the ``Append Client Journal"
mechanism). Bars above \(10^0\) are slower than the ``Append Client Journal"
mechanism and bars below are faster.  ``Stream" is an approximation of the
overhead and is calculated by subtracting the runtime of the job with the
journal turned off from the runtime with the journal turned on.  The largest
workload we tested is 100K file creates in the same directory.  This is the
maximum recommended size of a directory in CephFS; preliminary experiments with
larger directory sizes show memory problems.

\subsubsection{Poorly Scaling Data Structures} Despite doing the same amount of
work, mechanisms that rely on poorly scaling data structures have large
slowdowns for the larger number of creates. For example, ``RPCs" which relies
on the internal CephFS directory structures, goes from a \(40\times\) slowdown
for 10K files to a \(90\times\) slowdown for 100K files. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal ({\it e.g.} the persists, ``Volatile Apply") experience a
much less drastic slowdown because the journal data structure does not need to
be scanned for every operation.

@@

\noindent\textbf{Takeaway}: the CudeleFS mechanisms have overheads and costs
that can differ {\it by order of magnitude}. CudeleFS gives users the ability
to compose these mechanisms based on their application's correctness
requirements and performance goals.

\subsection{Weak vs. Strong Consistency}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Weak
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-allow-block.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/viz-blockallow.ipynb}{source}]
Using the ``allow" and ``block" API, users can isolate directories from
interfering clients. Performance with blocking turned is the same as
``isolated" from Figure~\ref{fig:overhead-b}.
\label{fig:slowdown-allow-block}}
\end{figure}

@@

>>>>

This paper adheres to The Popper
Convention\footnote{\url{http://falsifiable.us}}~\cite{jimenez_popper_2016}, so
experiments presented here are available in the repository for this
article\footnote{Links have been removed for double-blind submission}.
Experiments can be examined in more detail, or even re-run, by visiting the
\texttt{[source]} link next to each figure. That link points to a Jupyter
notebook that shows the analysis and source code for that graph, which points
to an experiment and its artifacts.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{
[\href{https://...}{source}]
The performance of the CudeleFS mechanisms normalized to the runtime of the
``Append Client Journal" mechanism (the runtime of writing \(n\) file creates
to the client's in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/behavior-journal-size.png}
\caption{
[\href{https://...}{source}]
In-memory client journal scales with the number of
updates.\label{fig:behavior-journal-size}}
\end{figure}

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the CudeleFS
mechanisms, normalized to the time it takes to write \(n\) file create updates
to the client's in-memory journal ({\it i.e.} the ``Append Client Journal"
mechanism). Bars above \(10^0\) are slower than the ``Append Client Journal"
mechanism.  ``Stream" is an approximation of the
overhead and is calculated by subtracting the runtime of the job with the
journal turned off from the runtime with the journal turned on.  The largest
workload we tested is 100K file creates in the same directory.  This is the
maximum recommended size of a directory in CephFS; preliminary experiments with
larger directory sizes show memory problems.

\subsubsection{Poorly Scaling Data Structures} Despite doing the same amount of
work, mechanisms that rely on poorly scaling data structures have large
slowdowns for the larger number of creates. For example, ``RPCs" which relies
on the internal CephFS directory structures, goes from a \(40\times\) slowdown
for 10K files to a \(90\times\) slowdown for 100K files. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal ({\it e.g.} the persists, ``Volatile Apply") experience a
much less drastic slowdown because the journal data structure does not need to
be scanned for every operation. Events are written to the end of the journal without
even checking the validity ({e.g.}, if the file already exists for a create),
which is another form of relaxed consistency because the file system assumes the
application has resolved conflicting updates in a different way.

@@

\noindent\textbf{Takeaway}: the CudeleFS mechanisms have overheads and costs
that can differ {\it by orders of magnitude}. CudeleFS gives users the ability
to compose these mechanisms based on their application's correctness
requirements and performance goals.

\subsection{Weak vs. Strong Consistency}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{
[\href{https://...}{source}]
The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Weak
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-allow-block.png}
\caption{
[\href{https://...}{source}]
Using the ``allow" and ``block" API, users can isolate directories from
interfering clients. Performance with blocking turned is the same as
``isolated" from Figure~\ref{fig:overhead-b}.
\label{fig:slowdown-allow-block}}
\end{figure}

@@

Figure~\ref{boner} scales the number of merges and shows linear performance.
The performance is linear for two reasons: (1) the merges are serialized and
(2) applying the updates to the in-memory metadata store does not touch data
structures that scale poorly. CudeleFS serializes merge requests
